---
title: "02_TEs_Outputs"
author: "Idalia Rojas"
date: "2024-02-12"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## REPET outputs

REPET pipeline to identify, classify and annotate TEs. REPET is executed in multiple step and produces an overwhelm number of outputs files. This script used the TE_classified and filtered output to extract and plot the results for Zymoseptoria passerinii. 


```{r libraries}
library(tidyverse)
```

## Load data

The REPET pipeline v2.5 was run for the 44 Illumina genomes,and the Class and family order data were extracted from the path  TEdenovo/${ProjectName}_Blaster_GrpRecPil_Map_TEclassif_Filtered/clasifConsensus/${ProjectName}_sim.classif_stats.txt, where ${ProjectName} is the corresponding isolates. 
The data was transferred to a single table and manually edited

```{r te.families, echo=FALSE}




```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
